% !TeX program = xelatex
% Run with XeLaTeX

\documentclass[
    changecolor={96, 52, 177},
]{peter-resume}
\begin{document}
\pagestyle{empty} %to remove the page numbers

% This is the header on the first page. It contains your name and contact
% details.
% \sep inserts a | between items.
% You can use FontAwesome icons and use \FAspace after a font awesome icon to
% insert a predefined horizontal space after a font awesome icon icon.
\header{Peter}{Le}{
  Software Development Engineer}{
  \faMapMarker \FAspace 1255 Harrison St Apt 132 Seattle, WA 98109}{
  \faMobile \FAspace +(602) 540 3272 \sep
  \faEnvelope \FAspace peterle271@gmail.com \sep
  \faHome \FAspace ptle.github.io \sep
  \faLinkedinSquare  \FAspace ptle27 \sep
  \faGithub \FAspace ptle
  }
\cvsection{Experience}
\cventry
  {Software Development Engineer II}
  {Amazon}
  {Seattle, Washington}
  {August 2018 - Present}
  {
    \begin{cvitems}
      \item {Software Developer on the Frustration Free Networking (FFN) team which is focused on minimizing customer frustration in device setup/networking}
      \item {Scrum master for current sub team. Ensured team followed agile methodology and properly prioritized business/engineering needs.}
      \item {Leading iOS integration into Amazon's main mobile shopping app so millions of customers can use our workflows for device setup/networking.}
      \item {Leveraged Native AWS technologies for logging and metrics capabilities that our team, internal stakeholders, and customers can use.}
    \end{cvitems}
  }
\cventry
  {Software Development Engineer}
  {}
  {}
  {}
  {
    \begin{cvitems}
      \item {Software Developer on the Device Software and Services team that is responsible for over the air (OTA) updates and backup/restore (BAR) for all Amazon Devices.}
      \item {Scaled, maintained, and implemented new features for services that vend updates and backups to millions of devices.}
      \item {Maintained and implemented new features for three client applications using Android (AOSP), Fire OS, and C.}
    \end{cvitems}
  }
\cventry
  {Software Development Engineer Intern}
  {Amazon}
  {Tempe, Arizona}
  {May 2017 - August 2017}
  {
    \begin{cvitems}
      \item {Intern for Seller Promotions teams that handle lightning deals and various promotions for Amazon Marketplace.}
      \item {Developed full stack application for business team using Java, HTML, CSS, Javascript, NoSQL, Coral services, and the Spring framework.}
    \end{cvitems}
  }
\cventry
  {Coding Instructor}
  {Codakid}
  {Scottsdale, Arizona}
  {May 2016 - August 2016}
  {
    \begin{cvitems}
      \item {Implemented and refined curriculum using Java and Javascript.}
      \item {Taught programming fundamentals to students of various ages through game development curriculum.}
    \end{cvitems}
  }

\cvsection{Education}
\cventry
  {Bachelor of Science in Computer Science; GPA: 4.0}
  {Arizona State University}
  {Tempe, Arizona}
  {August 2014 - May 2018}
  {
    \begin{cvitems}
      \item {Graduated Summa Cum Laude from Ira A. Fulton School of Engineering.}
      \item {Graduated from Barrett the Honors College with thesis: \it{Study of Hackathons through Desert Hacks}.}
    \end{cvitems}
  }

\cvsection{Accomplishments}
\cventry
  {Marketing Director \& Hacker Experience Director}
  {Sun Hacks \& Desert Hacks}
  {Tempe, Arizona}
  {June 2016 - May 2018}
  {
    \begin{cvitems}
      \item {Founding member of Arizona State's first official collegiate hackathon with Desert Hacks.}
      \item {Helped merge three different hackathon organizations into Sun Hacks to ensure future sustainability.}
      \item {Ensured hackers had optimal experience by handling day of logistics, such as volunteer management and obtaining anything hackers needed. Also, handled marketing through on-campus promotions, reaching out to other student organizations, and communicating with students that expressed prior interest.}
    \end{cvitems}
  }
\cventry
  {Teaching Assistant}
  {CodePath University}
  {Tempe, Arizona}
  {January 2017 - May 2017}
  {
    \begin{cvitems}
      \item {Instructed 12-week iOS course at Arizona State supplemented through CodePath University.}
      \item {Had weekly check-ins and prep work with CodePath University to ensure success of the program at Arizona State.}
      \item {Learned and developed various iOS apps using Swift, Xcode, and Cocoa framework whilst teaching/supporting other students.}
    \end{cvitems}
  }

\cvsection{Skills}
  \begin{cvskills}
    \cvskill{Languages:}{Java, Objective C, Swift, C, C++, Python, HTML, CSS, JavaScript, SQL}
    \cvskill{Frameworks:}{AWS, Bootstrap, Bulma, Cocoa, D3, Flask, Google App Engine, Flutter}
    \cvskill{Databases:}{SQL, NoSQL, PostgreSQL, MySQL}
  \end{cvskills}

\end{document}
